### 2015-10-06 compl.tex
Text improvements
Removed unused content

\begin{forrsi}
The following lemmas can be proved with a similar method.
%For the sake of brevity, the proofs are omitted.
\end{forrsi}
\item[Lemma 2]
{\bf A command \(create(\pi)\) can not precede a command  
\(remove(\piesub)\).} 
\begin{notrsi}
\emph{Proof.} 
This can be proved the same way, only
the base case differs; now 
\(create(\pi); remove({\piesub})\) equals \(break\) or expands 
to \(skip\) by Law \lawxvi~and \lawxxvii.
The induction step is the same.
\end{notrsi}

\item[Lemma 3]
{\bf A command \(remove(\piesub)\) can not precede a command
\(create(\pi)\).} 
\begin{notrsi}
\emph{Proof.} This can be proved similarly, in this 
case the base step is
\(remove(\piesub); create({\pi})\) equals \(break\) or
expands to \(edit\) (Law \lawxxi~and \lawxxviii);
in the induction step we can prove that if
\(S[j-1]=create(\pisup)\) precedes \(S[j]=create(\pi)\), according to
the induction hypothesis, \(S\eqexp break\) 
(we know that \(\pisup\prec\pi\)). Otherwise it would be possible to
shorten the sequence (which contradicts our precondition) or commuted (and therefore the induction hypothesis
still holds). (Laws \lawvii,
\lawviii, \lawxiv, \lawxv, \lawxx, \lawxxi, \lawxxviii.)
\end{notrsi}

\item[Lemma 4]
{\bf A command \(create(\piesub)\) can not precede a command
\(create(\pi)\).} 
\begin{notrsi}
\emph{Proof.} 
We obtain this result from Lemma 3: the base step is 
\(create(\piesub); create({\pi}) \equiv (\eqexp) break\) (Law 15); the
induction step is the same.
\end{notrsi}

\item[Lemma 5]
{\bf A command \(create(\piesub)\) can not precede a command
\(remove(\pi)\).} 
\begin{notrsi}
\emph{Proof.} 
Our base step now is 
\(S[j-1];S[j]=create({\piesub}); remove(\pi)\eqexp skip\) or equals
\(break\) according to Laws \lawxxvii~and \lawxvii.
But in our induction step, we go in the opposite direction and perform
analysis on \(S[i+1]\).
If \(S[i+1]=create({\piesub}_{sub})\) follows \(S[i]=create(\piesub)\),
the induction hypothesis applies, therefore \(S\eqexp break\). Otherwise
the commands could be simplified or commuted (Laws \lawxviii, \lawxiv,
\lawxv, \lawxvi, \lawxvii, \lawxxvii.)
\end{notrsi}

\item[Lemma 6] 
{\bf It is impossible that a command \(remove(\pi)\)
precedes a command \(create(\piesub)\).} 
\begin{notrsi}
\emph{Proof.} 
Now our base step is
\(remove(\pi); create(\piesub)\eqexp edit\) or equals to
\(break\) (Laws \lawxxviii~and \lawxx). In the induction step we
examine command \(S[i+1]\). 
If it's not commutable or simplifyable,
it can be only \(remove(\pisup)\).
In that case the induction hypothesis applies.
\end{notrsi}
\end{description}

@@

\begin{forrsi}
The following lemmas can be proved similarly.
\end{forrsi}
\item[Lemma E2] {\bf A command \(create(\pi)\) cannot precede a command 
\(edit(\pi)\).} 
\begin{notrsi}
\emph{Proof.} The same; last step is made according to
Lemma 2.
\end{notrsi}

\item[Lemma E3] {\bf A command \(remove(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\begin{notrsi}
\emph{Proof.} 
This proof is also very similar to the aboves. The base step is 
\(edit(\pi,\cdir{X}); remove(\pi)\equiv remove(\pi)\) (Law \lawxxv). In the
induction step we investigate command \(S[i+1]\). If it was not
\(create(\pisub)\), a commuting (or simplifying) law could be applied. If
it is, we have \(S\eqexp break\) according to Lemma 5.
\end{notrsi}

\item[Lemma E4] {\bf A command \(create(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\begin{notrsi}
\emph{Proof.} The same; last step
according to Lemma 4.
\end{notrsi}
\end{description}

@@

\item \(remove(\pi)\in S_0\implies remove(\pi)\in S'_0\).
\emph{Proof.} 
\begin{forrsi}
It can be done similarly to the case of \(create\).
\end{forrsi}
\begin{notrsi}
Now we can be sure that \(F(\pi)\ne\ud\) and
\(S_0G(\pi)=\ud\). If (instead of
\(remove\)) there was no command on \(\pi\) in \(S'_0\) then 
\(S'_0G(\pi)\ne\ud\)  would hold. In case of \(edit\), 
\(S'_0G(\pi)\ne\ud\) would hold (contradicting
\(S_0G(\pi)=\ud\)). \(create\) would break \(G\) since
\(G(\pi)\ne\ud\). Again, we have contradiction in all cases.
\end{notrsi}

@@

We obtain \(S_0^*\) and \(S^\prime_0^*\) by applying this method to \(S_0\) and
\(S^\prime_0\). Since they contain the same
commands, and the resulting order is the same,
\(S_0^*\) and
\({S^\prime_0}^*\) are \emph{exactly the same}. Now we have
\(S\eqexp S_0\eqexp S_0^*\equiv{S^\prime_0}^*\eqshr S^\prime_0\eqshr
S^\prime\), that is, \(S\eqifnbr S^\prime\). Our theorem is proved.

>>>>

\item[Lemma 2]
{\bf A command \(create(\pi)\) can not precede a command  
\(remove(\piesub)\).} 
\emph{Proof.} 
This can be proved the same way, only
the base case differs; now 
\(create(\pi); remove({\piesub})\) equals \(break\) or expands 
to \(skip\) by Law \lawxvi~and \lawxxvii.
The induction step is the same.

\item[Lemma 3]
{\bf A command \(remove(\piesub)\) can not precede a command
\(create(\pi)\).} 
\emph{Proof.} This can be proved similarly, in this 
case the base step is
\(remove(\piesub); create({\pi})\) equals \(break\) or
expands to \(edit\) (Law \lawxxi~and \lawxxviii);
in the induction step we can prove that if
\(S[j-1]=create(\pisup)\) precedes \(S[j]=create(\pi)\), according to
the induction hypothesis, \(S\eqexp break\) 
(we know that \(\pisup\prec\pi\)). Otherwise it would be possible to
shorten the sequence (which contradicts our precondition) or commuted (and therefore the induction hypothesis
still holds). (Laws \lawvii,
\lawviii, \lawxiv, \lawxv, \lawxx, \lawxxi, \lawxxviii.)

\item[Lemma 4]
{\bf A command \(create(\piesub)\) can not precede a command
\(create(\pi)\).} 
\emph{Proof.} 
We obtain this result from Lemma 3: the base step is 
\(create(\piesub); create({\pi}) \equiv (\eqexp) break\) (Law 15); the
induction step is the same.

\item[Lemma 5]
{\bf A command \(create(\piesub)\) can not precede a command
\(remove(\pi)\).} 
\emph{Proof.} 
Our base step now is 
\(S[j-1];S[j]=create({\piesub}); remove(\pi)\eqexp skip\) or equals
\(break\) according to Laws \lawxxvii~and \lawxvii.
But in our induction step, we go in the opposite direction and perform
analysis on \(S[i+1]\).
If \(S[i+1]=create({\piesub}_{sub})\) follows \(S[i]=create(\piesub)\),
the induction hypothesis applies, therefore \(S\eqexp break\). Otherwise
the commands could be simplified or commuted (Laws \lawxviii, \lawxiv,
\lawxv, \lawxvi, \lawxvii, \lawxxvii.)

\item[Lemma 6] 
{\bf It is impossible that a command \(remove(\pi)\)
precedes a command \(create(\piesub)\).} 
\emph{Proof.} 
Now our base step is
\(remove(\pi); create(\piesub)\eqexp edit\) or equals to
\(break\) (Laws \lawxxviii~and \lawxx). In the induction step we
examine command \(S[i+1]\). 
If it's not commutable or simplifyable,
it can be only \(remove(\pisup)\).
In that case the induction hypothesis applies.
\end{description}

@@

\item[Lemma E2] {\bf A command \(create(\pi)\) cannot precede a command 
\(edit(\pi)\).} 
\emph{Proof.} The same; last step is made according to
Lemma 2.

\item[Lemma E3] {\bf A command \(remove(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\emph{Proof.} 
This proof is also very similar to the aboves. The base step is 
\(edit(\pi,\cdir{X}); remove(\pi)\equiv remove(\pi)\) (Law \lawxxv). In the
induction step we investigate command \(S[i+1]\). If it was not
\(create(\pisub)\), a commuting (or simplifying) law could be applied. If
it is, we have \(S\eqexp break\) according to Lemma 5.

\item[Lemma E4] {\bf A command \(create(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\emph{Proof.} The same; last step
according to Lemma 4.
\end{description}

@@

\item \(remove(\pi)\in S_0\implies remove(\pi)\in S'_0\).
\emph{Proof.} 
Now we can be sure that \(F(\pi)\ne\ud\) and
\(S_0G(\pi)=\ud\). If (instead of
\(remove\)) there was no command on \(\pi\) in \(S'_0\) then 
\(S'_0G(\pi)\ne\ud\)  would hold. In case of \(edit\), 
\(S'_0G(\pi)\ne\ud\) would hold (contradicting
\(S_0G(\pi)=\ud\)). \(create\) would break \(G\) since
\(G(\pi)\ne\ud\). Again, we have contradiction in all cases.

@@

We obtain \(S_0^*\) and \({S^\prime}_0^*\) by applying this method to \(S_0\) and
\(S^\prime_0\). Since they contain the same
commands, and the resulting order is the same,
\(S_0^*\) and
\({S^\prime_0}^*\) are \emph{exactly the same}. Now we have
\(S\eqexp S_0\eqexp S_0^*\equiv{S^\prime_0}^*\eqshr S^\prime_0\eqshr
S^\prime\), that is, \(S\eqifnbr S^\prime\). Our theorem is proved.
